\chapter{Background}\label{chap:background}

To achieve this we are planning to use the below Amazon resources like  S3, DynamoDB, EC2 instances and Lambda function. 

\section{S3}

S3 - stands for Simple Storage Service. This service could be utilized to collect, store and analyze huge amounts of data. Data stored in S3 could be retrieved from anywhere. It provides comprehensive security and compliance capabilities. S3 is designed to deliver 99.999999999\% durability.\\

\subsection{Advantages:}\cite{S3documentation}
\begin{enumerate}
	\item Unmatched Durability, Availability, \& Scability
	\item Most comprehensive security \& compliance capabilities
	\item Query in place
	\item Flexible management
	\item Most supported by partners, vendors, \& AWS serices
	\item Easy, Flexible data transfer
\end{enumerate}

\section{Dynamo DB} \cite{DynamoDBDoc}
Amazon DynamoDB is a nonrelational database that delivers reliable performance at any scale.

\subsection{Advantages:}
\begin{enumerate}
	\item Performance at scale
	\item Fully managed
	\item Enterprise-ready
\end{enumerate}

\section{Elastic Compute Cloud (EC2)} \cite{EC2Doc}
Amazon Elastic Comput Cloud is a web service that provides secure, resizable compute capacity in the cloud. EC2 has changed the economics of computing by allowing companies to pay only for the capacity that is being utilized.

\subsection{Advantages:}
\begin{enumerate}
	\item Elastic web-scale computing
	\item Completely controlled
	\item Flexible cloud hosting services
	\item Integrated
	\item Reliable
	\item Secure
	\item Inexpensive
	\item Easy to start
\end{enumerate}

\section{Elastic Compute Cloud (EC2)} \cite{LambdaDoc}
AWS Lambda can run code without provisioning or managing servers. We have to pay only for the compute time consumed.

\subsection{Advantages:}
\begin{enumerate}
	\item No servers to manage
	\item Continuous scaling
	\item Subsecond metering
\end{enumerate}